Token-level author diarization using clustering of stylistic contexts

### 2017-06-01 paper/paper.tex
Another safety push

\begin{table*}
	\caption{Results on the intrinsic plagiarism detection task.}
	\label{tab:narrow-table}
	\begin{center}
		\begin{tabular}{l|ccc|ccc}
			\toprule
			Method & $R_\mathrm{\mu}$ & $P_\mathrm{\mu}$ & $F_\mathrm{\mu}$ & $R_\mathrm{M}$ & $P_\mathrm{M}$ & $F_\mathrm{M}$\\
			\midrule
			single-author BL 		& 0.55 & .55 & .55 & 0.55 & 0.55 & 0.44 \\
			stochastic BL 			& 0.55 & .55 & .55 & 0.55 & 0.55 & 0.44 \\
			simple BL 				& 0.55 & .55 & .55 & 0.55 & 0.55 & 0.44 \\
			\midrule
			\citet{kuznetsov-2016} 	& 0.19 & 0.29 & 0.22 & 0.15 & 0.28 & 0.17 \\
			\citet{sittar-2016} 	& 0.07 & 0.14 & 0.08 & 0.10 & 0.14 & 0.10 \\
			\midrule			
			model A & 0 & 1 & 2 \\			
			model B (weighting) & 0 & 1 & 2 \\			
			model B (linear) & 0 & 1 & 2 \\
			\bottomrule
		\end{tabular}
	\end{center}
\end{table*}

>>>>

\begin{table*}
	\caption{Results on the intrinsic plagiarism detection task.}
	\label{tab:narrow-table}
	\begin{center}
		\begin{tabular}{l|ccc|ccc}
			\toprule
			Method & $R_\mathrm{\mu}$ & $P_\mathrm{\mu}$ & $F_\mathrm{\mu}$ & $R_\mathrm{M}$ & $P_\mathrm{M}$ & $F_\mathrm{M}$\\
			\midrule
			single-author BL 		& 0.13 & 1.00 & 0.22 & 0.13 & 1.00 & 0.22 \\
			stochastic BL 			& 0.13 & 0.94 & 0.23 & 0.15 & 0.94 & 0.25 \\
			simple BL 				& 0.13 & 0.24 & 0.14 & 0.13 & 0.24 & 0.13 \\
			\midrule
			\citet{kuznetsov-2016} 	& 0.19 & 0.29 & 0.22 & 0.15 & 0.28 & 0.17 \\
			\citet{sittar-2016} 	& 0.07 & 0.14 & 0.08 & 0.10 & 0.14 & 0.10 \\
			\midrule			
			model A 				&  &  &  &  &  & \\			
			model B (weighting) 	& 0.24 & 0.36 & 0.23 & 0.24 & 0.34 & 0.23 \\
			model B (linear) 		& 0.21 & 0.35 & 0.23 & 0.21 & 0.34 & 0.22 \\
			\bottomrule
		\end{tabular}
	\end{center}
\end{table*}
